Parsing Postfix Log Files

### 2009-04-15 doc/logparser.tex
Corrections from proofreading.

\newcommand{\numberOFlogLINEShuman}[0]{%
    60.72 million%
}

@@

@@

    XXX REWRITE WHEN THESIS IS FINISHED\@.

    Parsing Postfix log files is much more difficult than it first appears,
    but it \textit{is\/} possible to achieve a high degree of accuracy in
    understanding Postfix log files and reconstructing the actions taken by
    Postfix that generated the log files.  This thesis describes the
    creation of a parser for Postfix log files, documenting the
    architecture developed and the parser implementing it, explaining the
    difficulties encountered and the solutions developed, with reference to
    an implementation that stores data gleaned from the log files in an SQL
    database.  The gathered data can be used to optimise current anti-spam
    measures, to produce statistics showing how effective those measures
    are, or to provide a baseline to test new anti-spam measures against.
    The Postfix log file parser needs to be very precise and strict when
    parsing, yet must allow users to easily adapt or extend it to parse new
    inputs, without requiring that the user have an in-depth knowledge and
    understanding of the parser's internal workings.  The newly developed
    architecture aims to make the process of parsing new inputs as simple
    as possible, enabling users to trivially add new rules (to parse
    variants of existing inputs) and relatively easily add new actions (to
    process a previously unknown category of inputs).  The architecture
    scales linearly or better as the number of rules and size of input
    increases, making it suitable for parsing large corpora or months of
    accumulated data.

>>>>

\newcommand{\numberOFlogLINEShuman}[0]{%
    60.722 million%
}

@@

\newcommand{\numberOFconnectionsINlogFILES}[0]{%
    13,850,793%
}

@@

    Parsing Postfix log files is much more difficult than it first appears,
    but it \textit{is\/} possible to achieve a high degree of accuracy in
    understanding Postfix log files, and subsequently in reconstructing the
    actions taken by Postfix when processing mail delivery attempts.  This
    thesis describes the creation of a parser for Postfix log files,
    documenting the architecture developed for this project and the parser
    that implements it, explaining the difficulties encountered and the
    solutions developed, with reference to an implementation that stores
    data gleaned from the log files in an SQL database.  The gathered data
    can be used to optimise current anti-spam measures, to produce
    statistics showing how effective those measures are, or to provide a
    baseline to test new anti-spam measures against.  The Postfix log file
    parser needs to be very precise and strict when parsing log files, yet
    must allow users to easily adapt or extend it to parse new log lines,
    without requiring that the user have an in-depth knowledge and
    understanding of the parser's internal workings.  The newly developed
    architecture is designed to make the process of parsing new inputs as
    simple as possible, enabling users to trivially add new rules (to parse
    variants of known inputs) and relatively easily add new actions (to
    process a previously unknown category of inputs).  The architecture
    scales linearly or better as the number of rules and size of input
    increases, making it suitable for parsing large corpora or months of
    accumulated data.
